1-methods-toys

### 2018-05-24 analysis/analyses/evaluate_toy/1-methods-toys.Rmd
rename description

method_descriptions <- map(method_names, ~get(paste0("description_", .))()) %>% set_names(method_names)

@@

```{r}
# results <- PRISM::qsub_lapply(names(method_descriptions), function(method_name) {
results <- purrr::map(method_names, function(method_name) {
  library(dyneval)

  cat("Processing ", method_name, "\n", sep="")
  method <- method_descriptions[[method_name]]
  params <- method_params[[method_name]]

@@

  # factory(function() {
    dyneval:::execute_evaluation(tasks, method, params, metrics = metric_names, timeout = 100)
  # }
  # )()
})
# }, qsub_environment = list2env(lst(method_descriptions, tasks, metric_names, method_params)), qsub_config = PRISM::override_qsub_config(memory = "10G", execute_before=c("module load python/x86_64/3.5.1"), wait=F))
```

>>>>

method_ti_methods <- map(method_names, ~get(paste0("ti_", .))()) %>% set_names(method_names)

@@

```{r}
# results <- PRISM::qsub_lapply(names(method_ti_methods), function(method_name) {
results <- purrr::map(method_names, function(method_name) {
  library(dyneval)

  cat("Processing ", method_name, "\n", sep="")
  method <- method_ti_methods[[method_name]]
  params <- method_params[[method_name]]

@@

  # factory(function() {
    dyneval:::execute_evaluation(tasks, method, params, metrics = metric_names, timeout = 100)
  # }
  # )()
})
# }, qsub_environment = list2env(lst(method_ti_methods, tasks, metric_names, method_params)), qsub_config = PRISM::override_qsub_config(memory = "10G", execute_before=c("module load python/x86_64/3.5.1"), wait=F))
```
